### 2013-07-19 paper.tex
omnomnom

Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:prelim_probstate}.  
% TODO change this
We then do a bunch of nonsense.

@@

\section{Notations}
For each positive integer $n$, let us define for convenience the strings
\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
and
\[
	\AA_n \defeq
	\begin{cases}
		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
	\end{cases}.
\]
By the way, let $\BB_n$ denote the set of binary strings of length $n$.

@@

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b$ of length $n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
\end{proposition}
\begin{proof}
	Left as exercise. (It should take about a minute.)
\end{proof}

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } b[1] + b[2] + \dots + b[i] = equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if } \exists 1 \le i \le n-1: \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
size(7cm);
real h = 0.7;
pen s = blue, t = red + dashed + 0.6;
pen dot_s = blue, dot_t = red;
int n = 8;
draw(currentpicture, (0,0)--(0,h/2)..\left( 0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
draw(currentpicture, (1,0)--(1,h/2)..\left( 1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
draw(currentpicture, (2,0)--(2,h/2)..\left( 2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
draw(currentpicture, (5,0)--(5,h/2)..\left( 5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
draw(currentpicture, (4,0)--(4,h), s);
dot(currentpicture, (4,h), dot_s);
draw(currentpicture, (7,0)--(7,h), s);
dot(currentpicture, (7,h), dot_s);
dot(currentpicture, (1, h/2), dot_s);
dot(currentpicture, (2, h/2), dot_s);
label(currentpicture, "1", (0,-1.5h), dir(90));
label(currentpicture, "s", (0,-0.8*h), dir(90));
label(currentpicture, "0", (1,-1.5h), dir(90));
label(currentpicture, "s", (1,-0.8*h), dir(90));
label(currentpicture, "0", (2,-1.5h), dir(90));
label(currentpicture, "s", (2,-0.8*h), dir(90));
label(currentpicture, "1", (3,-1.5h), dir(90));
label(currentpicture, "s", (3,-0.8*h), dir(90));
label(currentpicture, "0", (4,-1.5h), dir(90));
label(currentpicture, "s", (4,-0.8*h), dir(90));
label(currentpicture, "1", (5,-1.5h), dir(90));
label(currentpicture, "s", (5,-0.8*h), dir(90));
label(currentpicture, "1", (6,-1.5h), dir(90));
label(currentpicture, "s", (6,-0.8*h), dir(90));
label(currentpicture, "0", (7,-1.5h), dir(90));
label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{It looks hard until you actually draw it.  Then you LOL.}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.

@@

	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$.  Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel each $k$ times} if they have $k$ antennae in common.  Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because there can be no other structures inside these faces.  Furthermore, it is easy to see that any faces must be formed in this manner.

@@

\section{Main Result}
\label{sec:mainresult}
%I wish I had one.

>>>>

Because the technical description of the problem statement is quite involved, we devote the entirety of section \ref{sec:prelim} to preliminaries and defer the actual problem statement to section \ref{sec:prelim_probstate}.

% TODO change this
We then do a bunch of nonsense.

@@

\section{Notations}
For each positive integer $n$, let us define for convenience the strings
\[ \SS_n \defeq \underbrace{s \dots s}_{\text{$n$ $s$'s}} \] 
and the ``alternating'' string
\[
	\AA_n \defeq
	\begin{cases}
		\underbrace{sts\dots s}_{\text{$n$ letters}} & \text{if } n \equiv 1 \pmod{2} \\
		\underbrace{sts\dots t}_{\text{$n$ letters}} & \text{if } n \equiv 0 \pmod{2} \\
	\end{cases}.
\]
By the way, let $\BB_n$ denote the set of binary strings of length $n$.

@@

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b$ of length $n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
\end{proposition}
\begin{proof}
	Straightforward induction on $n$.  
\end{proof}

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } b[1] + b[2] + \dots + b[i] \equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if } \exists 1 \le i \le n-1: \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
		size(7cm);
		real h = 0.7;
		pen s = blue, t = red + dashed + 0.6;
		pen dot_s = blue, dot_t = red;
		int n = 8;
		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
		draw(currentpicture, (4,0)--(4,h), s);
		dot(currentpicture, (4,h), dot_s);
		draw(currentpicture, (7,0)--(7,h), s);
		dot(currentpicture, (7,h), dot_s);
		dot(currentpicture, (1, h/2), dot_s);
		dot(currentpicture, (2, h/2), dot_s);
		label(currentpicture, "1", (0,-1.5h), dir(90));
		label(currentpicture, "s", (0,-0.8*h), dir(90));
		label(currentpicture, "0", (1,-1.5h), dir(90));
		label(currentpicture, "s", (1,-0.8*h), dir(90));
		label(currentpicture, "0", (2,-1.5h), dir(90));
		label(currentpicture, "s", (2,-0.8*h), dir(90));
		label(currentpicture, "1", (3,-1.5h), dir(90));
		label(currentpicture, "s", (3,-0.8*h), dir(90));
		label(currentpicture, "0", (4,-1.5h), dir(90));
		label(currentpicture, "s", (4,-0.8*h), dir(90));
		label(currentpicture, "1", (5,-1.5h), dir(90));
		label(currentpicture, "s", (5,-0.8*h), dir(90));
		label(currentpicture, "1", (6,-1.5h), dir(90));
		label(currentpicture, "s", (6,-0.8*h), dir(90));
		label(currentpicture, "0", (7,-1.5h), dir(90));
		label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{It looks hard until you actually draw it.  Then you LOL.}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.

@@

	Let us now compose $M_a \defeq \MM(\ul a)$ and $M_b \defeq \MM(\ul b)$.  Two components (one from $M_a$ and one from $M_b$) are said to \emph{feel} each other $k$ times if they have $k$ antennae in common.  Notice that if any two components feel each other at least twice, then there exist two adjacent antennae, whence the composition of the map is zero because the two antenna combine to form an empty face.  Furthermore, it is easy to see that any faces must be formed in this manner.  In combination with the claim above, this implies the first case of the theorem.

@@

\section{The Caterpillar Theorem}
\label{sec:caterpillar}
We turn our attention to the case of $\ul r = \AA_n$.  Let us make a few definitions before proceeding.

Consider a composition of two maps $\MM_{\AA_n}( \ul a, \ul b)$ and the associated diagram $D$.  Let us make a few convenient definitions for the graphical structures.
\begin{definition*}
	A \emph{pocket} is a face, and its \emph{contents} are the connected components inside that face.
\end{definition*}
\begin{definition*}
	A \emph{fence} is a contiguous path which runs from the top of the boundary to the bottom of the boundary (i.e. paths between the labelled vertices).  The diagram is divided by these fences into \emph{pastures}, which will be numbered from left to right as $0$, $1$, \dots, $M$.
\end{definition*}
